Comparison of Catalogs

### 2024-07-19 compare/compare.qmd
+magn

|         LCV         | HECATE | Description |
|:-------------------:|:------:|:-----------:|
| mag_B (with errors) |  BT (with errors)      |             |
|       Kmag   |     K   | 2MASS band magnitude  (both)          |
|                     |        |             |
## Absorbsion

>>>>

```{python}
#| echo: false
mag_B_corr = round(compare_data(dt["mag_B"], dt["BT"],unc = dt["E_BT"])[3], 3)
Kmag_corr = round(compare_data(dt["Kmag"], dt["K"], unc = dt["E_K"])[3], 3)
```
|         LCV         | HECATE | Description | Pearson Correlation \[-1,1\] |
|:-------------------:|:------:|:-----------:|:----------------------------:|
| mag_B (with errors) |  BT (with errors) |             | `{python} mag_B_corr` |
|       Kmag          |     K              | 2MASS band magnitude (both) | `{python} Kmag_corr` |

```{python}
scatter_plot(dt["mag_B"], dt["BT"], yerr = dt["E_BT"])
scatter_plot(dt["Kmag"], dt["K"], yerr = dt["E_K"])
```
## Absorbsion
